\bf Forecast reconciliation: A geometric view with new insights on bias correction

### 2019-09-16 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Working Paper

\begin{definition}[Coherent subspace]\label{def:cohspace}
   The $m$-dimensional linear subspace $\mathfrak{s}\subset \mathbb{R}^n$ for which a some linear constraints hold for all $\bm{y}\in\mathfrak{s}$ is defined as the \emph{coherent subspace}.
\end{definition}

@@

Defining concepts such as coherence and reconciliation in geometric terms provides new insights into forecast reconciliation methods. We have also provided evidence that bias correction before reconciliation improves forecast accuracy compared to approaches that do not bias correct and/or do not use reconciliation. Our intention in proposing a geometric interpretation is also to provoke research into new areas. We now discuss three such possibilities.

>>>>

\begin{definition}[Coherent subspace]\label{def:cohspace}
   The $m$-dimensional linear subspace $\mathfrak{s}\subset \mathbb{R}^n$ for which some linear constraints hold for all $\bm{y}\in\mathfrak{s}$ is defined as the \emph{coherent subspace}.
\end{definition}

@@

Defining concepts such as coherence and reconciliation in geometric terms provides new insights into hierarchical forecasting methods. We have also provided evidence that bias correction before reconciliation improves forecast accuracy compared to approaches that do not bias correct and/or do not use reconciliation. Our intention in proposing a geometric interpretation is also to provoke research into new areas. We now discuss three such possibilities.
